\addcontentsline{toc}{chapter}{Abstract}

\begin{abstract}
In the grand scheme of a large Information Retrieval project, the work of our team will be that of performing text classification on both the tweet collections and their associated webpages. In order to accomplish this task, we will seek to complete three primary goals. We will begin by performing research to determine the best way to extract information that will be used to represent a given document. Following that, we will work to determine the best method to select features and then construct feature vectors. Our final goal is to use the information gathered previously to build an effective way to classify each document in the tweet and webpage collections. We intend for these classifiers to be built with consideration of the ontology developed for the IDEAL project.

The team assigned to perform this classification work last year researched various methods and tools that could be useful in accomplishing the goals we have set forth. Last year's team developed a system that was able to accomplish similar goals to those we have set forth with a promising degree of success. Our goal for this year is to improve upon their successes using new technologies such as Apache Spark. It is our hope that this will allow us to build a more optimized system capable of working with larger collections of tweets and webpages.

We also have several other goals for this semester's work in addition to improving on prior classification work. Two of those main goals include handling incremental data updates and performing evaluations as to the effectiveness of our classification system. We have designed our system with both of these in mind. Our approach to both of these goals are described in detail in this paper.

\foxComment{Should add about: incremental, running experiments, evaluations.}

\end{abstract}